A general Nullstellensatz for generalized spaces

### 2019-03-16 paper-qcoh.tex
Outline

% XXX outline and higher-order

@@

\section{Background}

@@

\section{The special case of Horn theories}

@@

\section{The generalization to the higher-order case}

@@

\section{Applications}

@@

* XXX Anmerken, dass wir in konstruktiver Metalogik arbeiten.

>>>>

\paragraph{Outline} In Section~\ref{sect:review}, we review background on the
internal language of toposes, internal geometric theories and classifying
toposes. Section~\ref{sect:main} contains proofs of the main theorems in the
full generality of geometric theories. Restricting to Horn theories allows for
a treatment which is more algebraic and less logical in flavor. For the benefit
of readers with a more algebraic background, we include a mostly self-contained
account of the Horn case as Section~\ref{sect:horn}. We generalize our main
theorems to the higher-order case in Section~\ref{sect:higher-order} and
conclude with applications in Section~\ref{sect:applications}.

Throughout we work in a constructive metatheory, to allow our results to be
interpreted internally to toposes.
\medskip

@@

\section{Background}
\label{sect:review}

@@

\section{The special case of Horn theories}
\label{sect:horn}

@@

\section{The generalization to the higher-order case}
\label{sect:higher-order}

@@

\section{Applications}
\label{sect:applications}

@@
